Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-06 ms.tex
caption

\begin{figure}
\includegraphics[width=\columnwidth]{vwSources.pdf}
\caption{\label{fig:vwSources} {it Top Panel:} Sources contributing to the total heating rate of the CNM, $\vwO$ ({\it black}), including stellar wind heating ({\it orange}), Ia supernovae ({\it green}), millisecond pulsars ({\it blue}), and compton heating ({\it pink}).  Each heating source varies with black hole mass $\Mbh$ calculated for average star formation histories from
  \citet{MosterNaab+:2013a} (see Appendix~\ref{app:windheat} for details).  {\it Bottom Panel:} The
  ratio of the total heating rate ($\dot{q}_{\rm heat} \propto v_{w}^{2}$) from the top panel to the radiating cooling rate
  ($|\dot{q}_{\rm rad}|$) at the stagnation radius.  Dashed lines and red color show the thermally unstable region defined by $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| < 1$, for which the assumption of steady-state flow would be violated.  {\bf BDM: remove the red - its tacky and will vary based on core/cusp.  Draw a dashed line across at heating ratio of 1.  change y axis labels!  move stars label in top panel}}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{eta.pdf}
\includegraphics[width=\columnwidth]{rs_rIa.pdf}
\caption{\label{fig:eta} {\it Top panel:} Parameter $\eta$
  characterizing stellar mass loss rate (eq.~[\ref{eq:q}]) as a
  function of black hole mass $\Mbh$, calculated for average star
  formation histories from \citet{MosterNaab+:2013a} (see
  Appendix~\ref{app:windheat} for details).  {\it Bottom panel:} Ratio
  of Ia radius to stagnation radius as a function of $\Mbh$.  The Ia
  radius calculated from equation~\eqref{eq:rIa} based on convolving
  the average star formation histories with the SN Ia DTD.  The
  stagnation radius is calculated from \eqref{eq:stag_simple} using
  the total heating rate for each $\Mbh$ shown in the top panel. }
\end{figure}

@@

A more readily addressable test is whether a steady-state accretion
picture is capable of explaining the large scatter of typically 2-3
orders of magnitude in the observed distribution of $L_{X}/L_{\rm
  edd}$ at fixed $M_{\bullet}$.  Scatter is expected to result from at
least two effects: (1) the order of magnitude difference between
$\dot{M}$ for core and cusp galaxies at fixed $v_w$ and $M_{\bullet}$
(Fig.~\ref{fig:bh_growth}) leads to a similar scatter of $\dot{M}$ due
to the variation in the Nuker stellar density profile $\Gamma$ at
fixed $M_{\bullet}$; (2) the strong sensitivity of the accretion rate
to the stellar wind velocity, $\dot{M}/\dot{M}_{\rm edd} \propto
v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively
(Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]) in
combination with the significant dependence of $v_w$ on stochastic
intermittency in the star formation history (Fig.~NICK).  The
combination of (1) and (2) is capable of explaining much of the
observed sample, especially considering that scatter in $L_{\rm X}$
due to variations in $\dot{M}$ is exacerbated by the expectation that
$\epsilon_{X} \propto \dot{M}$ for radiatively inefficient flows {\bf
  AG Challenge: Scatter in L_X is similar for cores and cusps in Perllegrini}.

>>>>

\begin{figure}
\includegraphics[width=\columnwidth]{vwSources.pdf}
\caption{\label{fig:vwSources} {\it Top Panel:} Sources contributing
  to the total heating rate of the CNM, $\vwO$ ({\it black}),
  including stellar wind heating ({\it orange}), Ia supernovae ({\it
    green}), millisecond pulsars ({\it blue}), and compton heating
  ({\it pink}).  Each heating source varies with black hole mass
  $\Mbh$ calculated for average star formation histories from
  \citet{MosterNaab+:2013a} (see Appendix~\ref{app:windheat} for
  details).  {\it Middle Panel:} The ratio of the total heating rate
  ($\dot{q}_{\rm heat} \propto v_{w}^{2}$) from the top panel to the
  radiating cooling rate ($|\dot{q}_{\rm rad}|$) at the stagnation
  radius. {\it Bottom panel} Parameter $\eta$ characterizing stellar
  mass loss rate (eq.~[\ref{eq:q}]) as a function of black hole mass
  $\Mbh$, calculated for average star formation histories from and the
  ratio of Ia radius to stagnation radius as a function of $\Mbh$.
  The Ia radius calculated from equation~\eqref{eq:rIa} based on
  convolving the average star formation histories with the SN Ia DTD.
  The stagnation radius is calculated from \eqref{eq:stag_simple}
  using the total heating rate for each $\Mbh$ shown in the top panel
  assuming a cusp galaxy ($\Gamma=0.8$).}
\end{figure}

% \begin{figure}
% \includegraphics[width=\columnwidth]{eta.pdf}
% \includegraphics[width=\columnwidth]{rs_rIa.pdf}
% \caption{\label{fig:eta} {\it Top panel:} Parameter $\eta$
%   characterizing stellar mass loss rate (eq.~[\ref{eq:q}]) as a
%   function of black hole mass $\Mbh$, calculated for average star
%   formation histories from \citet{MosterNaab+:2013a} (see
%   Appendix~\ref{app:windheat} for details).  {\it Bottom panel:} Ratio
%   of Ia radius to stagnation radius as a function of $\Mbh$.  The Ia
%   radius calculated from equation~\eqref{eq:rIa} based on convolving
%   the average star formation histories with the SN Ia DTD.  The
%   stagnation radius is calculated from \eqref{eq:stag_simple} using
%   the total heating rate for each $\Mbh$ shown in the top panel. }
% \end{figure}

@@

A more readily addressable test is whether a steady-state accretion
picture is capable of explaining the large scatter of typically 2-3
orders of magnitude in the observed distribution of $L_{X}/L_{\rm
  edd}$ at fixed $M_{\bullet}$.  Scatter is expected to result from at
least two effects: (1) the order of magnitude difference between
$\dot{M}$ for core and cusp galaxies at fixed $v_w$ and $M_{\bullet}$
(Fig.~\ref{fig:bh_growth}) leads to a similar scatter of $\dot{M}$ due
to the variation in the Nuker stellar density profile $\Gamma$ at
fixed $M_{\bullet}$; (2) the strong sensitivity of the accretion rate
to the stellar wind velocity, $\dot{M}/\dot{M}_{\rm edd} \propto
v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively
(Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]) in
combination with the significant dependence of $v_w$ on stochastic
intermittency in the star formation history (Fig.~NICK).  The
combination of (1) and (2) is capable of explaining much of the
observed sample, especially considering that scatter in $L_{\rm X}$
due to variations in $\dot{M}$ is exacerbated by the expectation that
$\epsilon_{X} \propto \dot{M}$ for radiatively inefficient flows {\bf
  AG Challenge: Scatter in $L_X$ is similar for cores and cusps in Perllegrini}.
